### 2019-08-05 README.Rmd
added another talking point

- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
- can I remove some of the sources from the references file that I am not going to use?

>>>>

- see email from Shar
- Have you heard of trelliscope: https://hafen.github.io/trelliscopejs/#trelliscope
- I think I may have convinced Adam to talk at graphics group if we end up scheduling graphics group on Thursday
- opinions on saving pdf files to github - if no - what to do?
- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
- can I remove some of the sources from the references file that I am not going to use?
- have you heard of: Journal of Data Science, Statistics, and Visualisation (jdssv.org)
